---
title: "Problem Set 01"
author: Your Name
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    keep_md: false
    theme: journal
    highlight: haddock
    toc: yes
    toc_depth: 4
    toc_float: yes
# Uncomment below to produce .pdf
#   pdf_document:
#     latex_engine: xelatex
#     keep_tex: false ## Change to true if want keep intermediate .tex file
#     toc: true
#     toc_depth: 3
#     dev: cairo_pdf
# knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding,
#  output_format = 'all')
#  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```




## Task 2
 

Assign the name "x" to an integer vector from 1 to 10. 

Generate an logical vector "z" which elements store whether x is greater than 
2 and smaller than 8.

Compute the number of times the above condition is true.

```{r task3}

x <- c(1:10)
x

z <- x > 2 & x < 8
z

sum(z)

sum(x > 2 & x < 8)
```

## Task 3

Given the data frame below, create a new column called "c" that contains the 
product of "a" and "b". Do this using `$` and `[` indexing (and maybe `names()`).
Remember, data frames are (special) lists! 


```{r task3}
df <- data.frame(
  a = c("a", "b", "c", "c", "a"),
  b = c("a", "c", "d", "c", "b")
)

```


Solution:


```{r task3_solution}
df$c <- df$a * df$b
```