
---

# Example: CLT Simulations

.title-wrap2[**Central Limit Theorem**]

.font90[Let $X_1, X_2, \dots, X_n$ be a sequence of independent and identically distributed
random variables with a common mean $\mu$ and variance $\sigma^2$. In other words, 
$n$ random samples drawn from a population distribution of arbitrary form and mean $\mu$ and variance $\sigma^2$.
Let $\bar{X}_n$ be the sample average. 

When $n \rightarrow \infty$, $\bar{X}_n$ converges to the population $\mu$ (.hl2[law of large numbers]).

The .hl[CLT] describes the stochastic behaviour around $\mu$ during the convergence.

Simplified, it says that for large $n$ the sampling distribution of $\bar{X}_n$ approximates a
normal distribution $N(\mu, \frac{\sigma^2}{n})$.

> If you repeatedly and randomly sample (with replacement) a "large" amount of 
observations from a population and calculate the mean each time, the  .hl[sampling distribution] 
of the means will approximate a normal distribution.


]
.font70[.hl[Tipp:] If you need a more thorough refresher, check [these](https://ocw.mit.edu/courses/mathematics/18-05-introduction-to-probability-and-statistics-spring-2014/readings/MIT18_05S14_Reading6b.pdf) lecture notes. 
The [Wikipedia article](https://en.wikipedia.org/wiki/Central_limit_theorem) is also fine in this case.]


---

# Example: CLT Simulations

- 

.hl2[Let's visualise the sampling distribution using functions, loops, and funcitonals!]

Take the simplest example of tossing a coin $n$-times, where each $X_i$ is an independent flip of a
biased coin with the probability $p_i$ of heads being $0.6$.

Summarizing the model: 

$X_i \sim Bern(\mu_i)$ with $\mu_i = p_i = 0.6$

Now, we use R to draw from the bernoulli distribution a large number of 
random samples (e.g. 1000) each having a size of $n$ (e.g. also 1000) and calculate the mean each time. 

---

# Example: CLT Simulations

.code60[
```{r}
set.seed(111) # for reproducibility


sample_dist <- function(n = 1000, p = 0.6, runs = 1000) { 

  samp_means <- tibble(mean = rep(NA, runs))

  for (i in 1:runs) {

    x <- rbinom(n, 1, p)
    samp_means$mean[i] <- mean(x)

  }

  ggplot(samp_means, aes(x = mean)) +
    geom_histogram(aes(y =..density..)) +
    stat_function(
      fun = dnorm,
      args = list(mean = mean(samp_means$mean), sd = sd(samp_means$mean))
    )

}

```
]
---

# Example: CLT Simulations

```{r}
sample_dist()
```

---

# Example: CLT Simulations

- 

---

# Simulations: Further Reading