---
title: "Session 3: Problem Set"
subtitle: Data Wrangling I
author: Solution
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    keep_md: false
    code_folding: hide
    theme: yeti
    highlight: textmate
    toc: yes
    toc_depth: 4
    toc_float: yes
# Uncomment below to produce .pdf
#   pdf_document:
#     latex_engine: xelatex
#     keep_tex: false ## Change to true if want keep intermediate .tex file
#     toc: true
#     toc_depth: 3
#     dev: cairo_pdf
# knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding,
#  output_format = 'all')
#  })
---

```{r setup, include=FALSE}
# install package management tool pacman
# install.packages("pacman")

pacman::p_load(
  tidyverse,
  rio,
  modelsummary
)


# The .csv wouldve had 200mb; .parquet is under  1mb. The power of compression.
unvotes <- import("unvotes.parquet")


knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Data Wrangling UN Votes

In this problem set, we will use data from the [unvotes](https://github.com/dgrtwo/unvotes)
package. It contains data for all countries voting history in the general assembly.

Here is a description of the data set:

| variable      | description                                                                                                                                                              |
|---------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| rcid          | The roll call id; used to join with un_votes and un_roll_call_issues                                                                                                     |
| country       | Country name, by official English short name                                                                                                                             |
| country_code  | 2-character ISO country code                                                                                                                                             |
| vote          | Vote result as a factor of yes/abstain/no                                                                                                                                |
| session       | Session number. The UN holds one session per year; these started in 1946                                                                                                 |
| importantvote | Whether the vote was classified as important by the  U.S. State Department report "Voting Practices in the United Nations".  These classifications began with session 39 |
| date          | Date of the vote, as a Date vector                                                                                                                                       |
| unres         | Resolution code                                                                                                                                                          |
| amend         | Whether the vote was on an amendment; coded only until 1985                                                                                                              |
| para          | Whether the vote was only on a paragraph and not a resolution; coded only until 1985                                                                                     |
| short         | Short description                                                                                                                                                        |
| descr         | Longer description                                                                                                                                                       |
| short_name    | Two-letter issue codes                                                                                                                                                   |
| issue         | Descriptive issue name, 6 issues                                                                                                                                                   |

Source: [tidytuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-23/readme.md).

# Task 1

Familiarize yourself with the data. What's each variables type/class?

```{r}
str(unvotes)
glimpse(unvotes)

```

What is the level of observation of this data set?


**Answer:** 

> country-roll-call/date

Is this data set tidy?

**Answer:** 

> No, because not every type of observational unit is in its own table.

> We have three observational types/levels:

> - country-roll-call level (how each country voted in a certain roll call)
> - roll-call level
> - issue-level (infos on different issues)

> But it's only not tidy because I already merged the relational tables of the original data. I.e.
the **countries vote history** with details on **each roll call** (incl. the session date) and information
on the **issue** of each roll call. 

# Task 2

## a)

With
```{r}
datasummary_skim(unvotes$issue, type = "categorical")
```
you get a quick summary for the categorical issue variable.

However, as each `rcid` occurs multiple times for each country, the issues are,
of course, also repeatedly present in our data.

What we want is a **sorted** table for the distribution of our issue variable 
over all roll calls.

Create such table/tibble/data frame using **only** tidyverse verbs/functions (scroll to the bottom of this document if you need a hint).

```{r task1}

# There are several different ways we can achieve this:

# 1. E.g. using count() which is a shorthand for group_by(x) %>% summarise(n = n())

# count() returns a tibble of the form

# >        x        n
# >    <chr>    <int>
# >  1     A       35

# So we can just add a column to this computing the relative frequency:
unvotes %>%
  distinct(rcid, issue) %>%
  count(issue) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>% # sum() of the n vector/variable
  arrange(desc(percent))

# Another way:

unvotes %>%
  distinct(rcid, issue) %>%
  group_by(issue) %>%
  summarise(n = n()) %>% 
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  arrange(desc(percent))

# Yet another way

unvotes %>%
  distinct(rcid, issue) %>%
  group_by(issue) %>%
  transmute(n = n()) %>%
  unique() %>%
  ungroup() %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  arrange(desc(percent))

```

## b) 

Which issue category has the highest share of important votes?

```{r}
unvotes %>%
  distinct(rcid, issue, .keep_all = T) %>%
  group_by(issue) %>%
  summarise(votes = n(), 
  imp_votes = sum(importantvote, na.rm = TRUE), 
  share_imp = sum(importantvote, na.rm = TRUE) / n()) %>%
  arrange(desc(share_imp))
  
```

# Task 3


## a) 

Add variables that show, for each country, the number and share of "yes", "no", and "abstain" votes, 
pooled over all years. Additionally, put out a tibble/data frame with one 
row for each country and these new variables. 

```{r}
# First, add the variables:

unvotes <- unvotes %>%
  group_by(country) %>%
  mutate(n_votes = n(),
         pct_yes = sum(vote == "yes", na.rm = T)/n(),
         pct_no = sum(vote == "no", na.rm = T)/n(),
         pct_abs = sum(vote == "abstain", na.rm = T)/n())

# Next, compute a summary table

sum_tab_a <- unvotes %>%  # or use mean()
  distinct(country, .keep_all = TRUE) %>%
  select(country, n_votes, pct_yes, pct_no, pct_abs)
sum_tab_a

# OR

sum_tab_a_1 <- unvotes %>%
  group_by(country) %>%
  summarise(
    n_votes = n(),
    pct_yes = sum(vote == "yes", na.rm = T) / n(),
    pct_no = sum(vote == "no", na.rm = T) / n(),
    pct_abs = sum(vote == "abstain", na.rm = T) / n()
  )
sum_tab_a_1

```

## b) 

Calculate, for each country and issue, the number and share of "yes" votes but 
only for "important votes" and for the [permanent members](https://www.un.org/securitycouncil/content/current-members) 
of the security council. The output should have 30 rows.

```{r}

str(unvotes$importantvote)


perm_members <- c("United States", "Russia", "France", "United Kingdom", "China")

imp_votes_tab <- unvotes %>%
  group_by(country, issue) %>%
  filter(importantvote == 1, country %in% perm_members) %>%
  summarise(
    n_votes = n(),
    pct_yes = sum(vote == "yes", na.rm = T) / n()
  )
imp_votes_tab

```


## c) 

Get the years with the highest and lowest share of "yes" votes for 
each country.


```{r}

max_min_tab <- unvotes %>%
  filter(country %in% perm_members) %>%
  group_by(year = lubridate::year(date), country) %>% # lubridate is not loaded by default
  summarise(
    n_votes = n(),
    pct_yes = sum(vote == "yes", na.rm = T) / n()
  ) %>%
  ungroup() %>%
  group_by(country) %>%
  filter(pct_yes == max(pct_yes) | pct_yes == min(pct_yes)) %>%
  arrange(country, desc(pct_yes))
max_min_tab
```


# Hints:

Task 2a: `distinct()` may be helpful here!

Task 2b: Check out the arguments of `distinct()`!