---
title: "Lys"
subtitle: "goes Xaringan"
author:
  - "Markus Freitag"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    includes:
      after_body: "helpers/handw.js"
    css: ["default", "helpers/lys.css", "helpers/lys-fonts.css"]
    nature:
      beforeInit: "macros.js"
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
    seal: false
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(
  fig.align = "center",
  fig.retina = 2,
  cache = F # , echo=F, warning=F, message=F
)

# knitr::opts_chunk$set(fig.dim=c(4.8, 4.5), fig.retina=2, out.width="100%")

# install package management tool pacman
# install.packages("pacman")

# devtools::install_github("CorrelAid/datenguideR")

pacman::p_load(
  tidyverse,
  showtext,
  dagitty,
  ggdag,
  data.table,
  patchwork,
  rvest
)


# font_add_google(
#   name = "IBM Plex Sans",
#   family = "plex"
# )

# showtext_auto()



knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)
```


```{r set-ggplot-theme, include=FALSE}

theme_set(theme_classic() +
  theme(
    text = element_text(family = "plex", size = 25, colour = "#415564"),
    panel.background = element_rect(fill = "#f6f3f2"),
    plot.background = element_rect(fill = "#f6f3f2", color = "#f6f3f2"),
    panel.grid.major = element_line(colour = "#e8e8e8"),
    panel.grid.minor = element_blank(),
    legend.background = element_rect(fill = "#f6f3f2"),
    legend.box.background = element_rect(fill = "#f6f3f2"),
    axis.text = element_text(colour = "#415564"),
    axis.line = element_line(colour = "#415564"),
    axis.title = element_text(colour = "#415564"),
    axis.ticks = element_line(colour = "#415564"),
  ))

purple <- "#644155"
```


```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble(pen_color = purple)
```


class: inverse, center, title-slide, middle

<style> .title-slide .remark-slide-number {
  display: none;
} </style>

# .title-wrap[Intro to Programming with R for Political Scientists]

<br />

## Session 3: Data Wrangling

### Markus Freitag

### Geschwister Scholl Institute of Political Science, LMU

### [`r icons::icon_style(icons::fontawesome("twitter"), fill = "#415564")`](https://twitter.com/MarkusGFreitag) [`r icons::icon_style(icons::fontawesome("globe"), fill = "#415564")`](https://markusfreitag.netlify.app/)


### `r Sys.Date()`

<a href="https://github.com/m-freitag" class="github-corner" aria-label="View
source on Github"><svg width="80" height="80" viewBox="0 0 250 250"
style="fill:#415564; color:#f6f3f2; position: absolute; top: 0; border: 0;
right: 0;" aria-hidden="true"><path d="M0,0 L115,115 L130,115 L142,142 L250,250
L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6
C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9
125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor"
style="transform-origin: 130px 106px;" class="octo-arm"></path><path
d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2
139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2
159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2
C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2
216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4
203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9
156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z"
fill="currentColor"
class="octo-body"></path></svg></a><style>.github-corner:hover
.octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes
octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media
(max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner
.octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>

---

layout:true

<div class="my-footer"><span>Session 3: Data Wrangling</span></div>

---

# Overview

1. Intro

2. R-Studio and (Git)Hub

3. Base R & Tidyverse Basics

4. .hl[Data Wrangling]

5. Data Viz

6. Writing Functions

7. A complete scientific workflow with R

---

# Importing Data











```{r print pdf, include=FALSE}
# pagedown::chrome_print("./02_Data_Wrangling.html")
```
